XXXXX

### 2014-12-17 paper/RDF validation requirements/RDF validation requirements.tex
RDF Validation Requirements chapter
Context-Specific Exclusive OR of Properties
work on DL expressions for constraints starting at 36, some small improvements on earlier points

%\usepackage{amsmath}
\usepackage{amsmath, amssymb}
\usepackage{mathabx}

@@

% Todos
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\tb}[1]{\todo[size=\small, color=blue!40]{\textbf{Thomas:} #1}}
\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
\newcommand{\an}[1]{\todo[size=\small, color=green!40]{\textbf{Andreas:} #1}}
\newcommand{\er}[1]{\todo[size=\small, color=red!40]{\textbf{Erman:} #1}}

@@

\begin{DL}
Disjoint(parentOf, childOf)
\end{DL}

@@

\begin{DL}
Male $\sqcap$ Female $\sqsubseteq$ $\perp$
\end{DL}

@@

\begin{DL}
$\top$ $\sqsubseteq$ $\forall$ sonOf . Parent 
\end{DL}

@@

\begin{DL}
parentOf $\equiv$ $childOf^{-}$ \\
\end{DL}

@@

\begin{DL}
$A \equiv \forall foaf:name . xsd:string$ \\
$B \equiv \forall foaf:givenName . xsd:string$ \\
$C \equiv A XOR B$ \\
$D \equiv \forall foaf:mbox . xsd:string$ \\
$Human \equiv C \sqcap D$ \\
\end{DL}
\er{Where does this using $foaf:$ in DL come from? We need a description.}
\section{Context-Specific Exclusive OR of Properties}

@@

@@

\begin{DL}
1-23 $\equiv$ \{'1'\} $\sqcup$ \{'2'\} $\sqcup$ ... $\sqcup$ \{'23'\} \\
$\top$ $\sqsubseteq$ $\forall$ position . 1-23 \\
\end{DL}

@@

@@

@@

@@

@@

@@

@@

@@

@@

\begin{DL}
julia = john \\
\end{DL}

@@

\begin{DL}
julia $\ne$ john
\end{DL}

@@

\begin{DL}
:hasBrother $\sqsubseteq$ :hasMaleSibling $\sqcap$ :hasMaleSibling $\sqsubseteq$ :hasBrother \\
\end{DL}

@@

\begin{DL}

\end{DL}

\tb{ToDo: DL}

@@

\begin{DL}
:hasAge ( :Meg , "17"^^xsd:integer ) \\
\end{DL}

@@

\begin{DL}
owl:Thing $\sqsubseteq$ $\leq$ 1 :hasFather
\end{DL}

@@

\begin{DL}

\end{DL}

\tb{ToDo: DL}

@@

\begin{DL}

\end{DL}

\tb{ToDo: DL}

@@

@@

\begin{DL}

\end{DL}

\tb{ToDo: DL}

@@

@@

>>>>

%\usepackage{amsmath}
\usepackage{amsmath, amssymb}
\usepackage{examplep}
\usepackage{mathabx}

@@

% Todos
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\tb}[1]{\todo[size=\small, color=blue!40]{\textbf{Thomas:} #1}}
\newcommand{\ke}[1]{\todo[size=\small, color=orange!40]{\textbf{Kai:} #1}}
\newcommand{\an}[1]{\todo[size=\small, color=green!40]{\textbf{Andy:} #1}}
\newcommand{\er}[1]{\todo[size=\small, color=red!40]{\textbf{Erman:} #1}}

@@

\begin{DL}
Disjoint(parentOf, childOf)\\
Alternative:\\
$parentOf \sqsubseteq \neg childOf$
\end{DL}

@@

\begin{DL}
Male $\sqcap$ Female $\sqsubseteq$ $\perp$\\
Alternative:\\
$Male \sqsubseteq \neg Female$
\end{DL}

@@

\begin{DL}
$\top$ $\sqsubseteq$ $\forall$ sonOf . Parent \\
Equivalent to:\\
$\exists sonOf\sp{\overline{\ }}.\top \sqsubseteq Person$
\end{DL}

@@

\begin{DL}
parentOf $\equiv$ $childOf^{-}$ \\
not sure if this should be rather\\
$parentOf \sqsubseteq childOf^{-}$ \\
\end{DL}

\an{not sure!}

@@

\begin{DL}
$A \equiv \forall foaf:name . xsd:string$ \\
$B \equiv \forall foaf:givenName . xsd:string$ \\
$C \equiv A XOR B$ \\
$D \equiv \forall foaf:mbox . xsd:string$ \\
$Human \equiv C \sqcap D$ \\
\end{DL}
\er{Where does this using $foaf:$ in DL come from? We need a description.}

\an{I think we should use the existential quantifier instead of the universal quantifier!?}
\begin{DL}
$A \sqsubseteq \exists name.xsd:string$ \\
$B \sqsubseteq \exists givenName.xsd:string$ \\
$D \sqsubseteq \exists mbox.xsd:string$ \\
$Human \sqsubseteq C \sqcap D$ \\
\end{DL}

\section{Context-Specific Exclusive OR of Properties}

@@

\begin{DL}
NOT EXPRESSIBLE IN DL!!!
\end{DL}

@@

\begin{DL}
1-23 $\equiv$ \{'1'\} $\sqcup$ \{'2'\} $\sqcup$ ... $\sqcup$ \{'23'\} \\
$\top$ $\sqsubseteq$ $\forall$ position . 1-23 \\
This is just an auxiliary construction and is not sufficient for general cases, so: NOT EXPRESSIBLE IN DL!!!
\end{DL}

@@

\begin{DL}
I'm not sure about the meaning of this constraint, but for me this seams like e.g. the range of a role... but if this is the case, take into account the consequences of reasoning with OWA...
\end{DL}

\an{not sure!}

@@

\begin{DL}
I'm not sure about the meaning of this constraint, but for me this seams like e.g. the domain of a role... but if this is the case, take into account the consequences of reasoning with OWA...
\end{DL}

\an{not sure!}

@@

\begin{DL}
$Person \sqsubseteq \exists hasAncestor.Person$
\end{DL}

@@

\begin{DL}
$\exists hasAncestor.Person \sqsubseteq Person$ \\
(same as the definition of domains)
\end{DL}

@@

\begin{DL}
Not sure about the meaning of this constraint...
\end{DL}

\an{not sure!}

@@

\begin{DL}
- condition: universal quantification on object and data properties\\
\ \ \ \ same as above!?\\
- condition: existential quantification on object and data properties\\
\ \ \ \ same as above!?\\
- condition: if specific properties are present, then specific other properties also have to be present
\ \ \ \ same as super properties, so if a property (role or attribute) is used, all super properties are also present
\end{DL}

@@

\begin{DL}
$JediMentor \sqsubseteq \neg(\exists studentOf.JediMentor)$
\end{DL}

@@

\begin{DL} 
$\rho(\textsf{hasBirthday}) \sqsubseteq \PVerb{xsd:dateTime}$\\
(equal to the definition of an attribute (data property) range)
\end{DL}

@@

\begin{DL}
$\{julia\} = \{john\} $\\
\end{DL}

@@

\begin{DL}
$\{julia\} \ne \{john\} $\\
(this is by default because of the UNA)
\end{DL}

@@

\begin{DL}
:hasBrother $\sqsubseteq$ :hasMaleSibling $\sqcap$ :hasMaleSibling $\sqsubseteq$ :hasBrother \\
equivalent to: $hasBrother = hasMaleSibling$
\end{DL}

@@

\begin{DL}
$hasSon(\textbf{Peter},\textbf{Meg})$\\
(negation of such an assertion is not necessary / meaningless!)
\end{DL}

@@

\begin{DL}
$hasAge ( \textbf{Meg} ,\textbf{ "17"}\hat{\ } \hat{\ } xsd:integer ) $\\
\end{DL}

@@

\begin{DL}
$(\textsf{funct } \textsf{hasFather})$
\end{DL}

@@

\begin{DL}
$(\textsf{funct } \textsf{hasFather}\sp{\overline{\ }})$
\end{DL}

@@

\begin{DL}
Not sure about the meaning of this constraint...\\
May be it is:\\
$Shortcut \sqsubseteq \exists fatherOf.\{\textbf{Stewie}\}$
\end{DL}

\an{not sure!}

@@

\begin{DL}
Not sure about if this constraint is expressible in DL, I think not!
\end{DL}

\an{not sure!}

@@

\begin{DL}
Not sure if this is expressible in DL, may be we should have a detailed look to \textit{DL-Lite}$_{\mathcal{A},id}$ \\
(see \url{http://www.dis.uniroma1.it/~lembo/papers/calv-etal-RW-2009.pdf})
\end{DL}

\an{not sure!}

@@

\begin{DL}
Not sure if this is expressible in DL, I think not!
\end{DL}

\an{not sure!}

@@

\begin{DL}
Not sure if the meaning of this constraint, probably it is the same as for cardinality restrictions?
\end{DL}

\an{not sure!}
